Low Complexity Adaptive Sonar Imaging

### 2018-02-24 LCAforActiveSonarImaging/document.tex
Adding HRUIonGPU article

\ifPhdDoc
   \begin{figure}[tbp]\centering%
   \includegraphics[width=\linewidth]{gfx/fig1.eps}%
\else
   \begin{figure}[tbp]\centering%
   \ifPeerReview%
      \includegraphics[width=.5\linewidth]{gfx/buske1_online.eps}%
   \else%
      \includegraphics[width=\linewidth]{gfx/buske1_online.eps}%
\fi\fi%
\caption{Each Kaiser window is steered in the interval $\phi\in[0, \phi_{\mathrm{3\,dB}}(\beta)]$. The angle $\phi_{\mathrm{3\,dB}}(\beta)$ is the amount of steering needed for the steered amplitude response to have a \protect\minus{}3\,dB crossing that is exactly half that of the unsteered window. With each window steered this way we expect the resolution gain to remain predictable and independent of $\beta$, and we also effectively constrain the white noise gain of the beamformer.}\label{windows_steering}
\end{figure}

\ifPhdDoc
   \begin{figure}[tbp]\centering%
   \includegraphics[width=\linewidth]{gfx/fig2.png}%
\else
   \begin{figure}[tbp]\centering%
   \ifPeerReview%
      \includegraphics[width=.5\linewidth]{gfx/buske2_online.png}%
   \else%
      \includegraphics[width=\linewidth]{gfx/buske2_online.png}%
\fi\fi%
\caption{The submerged object used to test beamforming resolution is a 1\,m by 1\,m test cross attached to an anchor with a diameter of approximately 13\,cm. Source image curtesy of Bundeswehr Technical Center for Ships and Naval Weapons, Maritime Technology and Research (WTD 71).}\label{cross}
\end{figure}

\setcounter{topnumber}{1}
\setcounter{dbltopnumber}{1}

\ifPhdDoc
   \begin{figure*}[tbp]\centering%
   \includegraphics[width=\linewidth]{gfx/fig3.pdf}%
\else
   \begin{figure*}[t]\centering%
   \includegraphics[width=\linewidth]{gfx/buske3_online.pdf}%
\fi%
\caption{\emph{Determining LCA window type}: MVDR image with typical frequency responses for windows used in various pixel regions.\newline
\emph{Left:}\hfill
\parbox[t]{.95\linewidth}{MVDR sectorscan image of the oiltanker Holmengraa, with 40x40 pixel groups for the shadow, highlight and speckle region of the image indicated with red boxes.}\protect\\\hspace{\textwidth}
\emph{Right:}\hfill
\parbox[t]{.95\linewidth}{MVDR window amplitude and phase responses computed from the 40x40 pixel groups. The responses are overlayed each other and the amount of overlap is colored using a logarithmic scale. The size of the pixel groups were chosen ad-hoc for the histograms to be visually invariant to a shift in position within the same region. Since each pixel is pre-delayed into focus the unsteered responses all have their center at broadside. The dashed red lines at -13\,dB and -43\,dB marks the peak sidelobe levels of an unsteered rectangular and Hamming window, respectively. Note how the responses are more or less symmetric, with very little steering in the shadow, moderate steering in speckle and steering within roughly 3\,dB in highlight. The phase varies most in the highlight region where we see the highest contrast.} }\label{mvdr_selected_windows}
\end{figure*}

\ifPhdDoc
   \begin{figure*}[tbp]\centering%
   \includegraphics[width=\linewidth]{gfx/fig4.pdf}%
\else
   \begin{figure*}[t]%
   \includegraphics[width=\textwidth]{gfx/buske4_online.pdf}%
\fi%
\caption{\emph{Determining Kaiser parameter boundaries}: LCA images of the resolution test cross and anchor created with a large window database, but where the upper bounds for $\beta$ and $\phi$ are varied. The upper left image is equal to DAS with a rectangular window. For all images we measure the lateral distance $\Delta x$ between the two \protect\minus{}3\,dB points of the anchor (red object). These are specified relatively to the reference distance  $\Delta x_\text{ref}$ from the upper left DAS image.
\newline
\emph{Upper bound $\beta$:}\hfill
\parbox[t]{.89\linewidth}{Observe that LCA gets better at suppressing sidelobes in the image as we increase the upper bounds for $\beta$. \Fig{mvdr_selected_windows} suggests that MVDR prefers windows with sidelobe levels lower than that of Kaiser with $\beta=2$, but here we observe further improvement going to $\beta=5$.}\newline
\emph{Upper bound $\phi$:}\hfill
\parbox[t]{.89\linewidth}{As we increase the upper bound of the steering $\phi$, we also increase the lateral image resolution. }
}\label{oversampling_mosaic_bounds}
\end{figure*}

@@

\ifPhdDoc
   \begin{figure*}[tbp]\centering%
   \includegraphics[width=\linewidth]{gfx/fig6.pdf}%
\else
   \begin{figure*}[t]%\centering%
   \includegraphics[width=\textwidth]{gfx/buske6_online.pdf}%
\fi
\caption{\emph{LCA images using different window database sizes}. The window boundaries are the same. The upper left image is identical to a rectangularly weighted DAS. Observe that finer sampling of the $\beta$-range improves sidelobe suppression but leaves resolution unchanged. Adding more steering-variations improves both sidelobe suppression and resolution. However, using more than  $N_\beta=2$ window types and $N_\phi=3$ steering angles makes minimal difference.}\label{oversampling_mosaic}
\end{figure*}

@@

\appendices

>>>>

\ifPhdDoc
   \begin{figure}[tbp]\centering%
   \includegraphics[width=.8\linewidth]{gfx/fig1.eps}%
\else
   \begin{figure}[tbp]\centering%
   \ifPeerReview%
      \includegraphics[width=.5\linewidth]{gfx/buske1_online.eps}%
   \else%
      \includegraphics[width=\linewidth]{gfx/buske1_online.eps}%
\fi\fi%
\caption{Each Kaiser window is steered in the interval $\phi\in[0, \phi_{\mathrm{3\,dB}}(\beta)]$. The angle $\phi_{\mathrm{3\,dB}}(\beta)$ is the amount of steering needed for the steered amplitude response to have a \protect\minus{}3\,dB crossing that is exactly half that of the unsteered window. With each window steered this way we expect the resolution gain to remain predictable and independent of $\beta$, and we also effectively constrain the white noise gain of the beamformer.}\label{windows_steering}
\end{figure}

\ifPhdDoc
   \begin{figure}[tbp]\centering%
   \includegraphics[width=.7\linewidth]{gfx/fig2.png}%
\else
   \begin{figure}[tbp]\centering%
   \ifPeerReview%
      \includegraphics[width=.5\linewidth]{gfx/buske2_online.png}%
   \else%
      \includegraphics[width=\linewidth]{gfx/buske2_online.png}%
\fi\fi%
\caption{The submerged object used to test beamforming resolution is a 1\,m by 1\,m test cross attached to an anchor with a diameter of approximately 13\,cm. Source image curtesy of Bundeswehr Technical Center for Ships and Naval Weapons, Maritime Technology and Research (WTD 71).}\label{cross}
\end{figure}

\ifPhdDoc
   \begin{figure*}[tbp]\centering%
   \includegraphics[width=\linewidth]{gfx/fig3_phd.pdf}%
   \caption{\emph{Determining LCA window type}: MVDR image with typical frequency responses for windows used in various pixel regions.\\[.5\baselineskip]
   \textbf{Left:} MVDR sectorscan image of the oiltanker Holmengraa, with 40x40 pixel groups for the shadow, highlight and speckle region of the image indicated with red boxes.\\[.5\baselineskip]
   \textbf{Right:} MVDR window amplitude and phase responses computed from the 40x40 pixel groups. The responses are overlayed each other and the amount of overlap is colored using a logarithmic scale. The size of the pixel groups were chosen ad-hoc for the histograms to be visually invariant to a shift in position within the same region. Since each pixel is pre-delayed into focus the unsteered responses all have their center at broadside. The dashed red lines at -13\,dB and -43\,dB marks the peak sidelobe levels of an unsteered rectangular and Hamming window, respectively. Note how the responses are more or less symmetric, with very little steering in the shadow, moderate steering in speckle and steering within roughly 3\,dB in highlight. The phase varies most in the highlight region where we see the highest contrast.}\label{mvdr_selected_windows}
\else
\setcounter{topnumber}{1}
\setcounter{dbltopnumber}{1}

   \begin{figure*}[t]\centering%
   \includegraphics[width=\linewidth]{gfx/buske3_online.pdf}%
   \caption{\emph{Determining LCA window type}: MVDR image with typical frequency responses for windows used in various pixel regions.\newline
   \emph{Left:}\hfill
   \parbox[t]{.95\linewidth}{MVDR sectorscan image of the oiltanker Holmengraa, with 40x40 pixel groups for the shadow, highlight and speckle region of the image indicated with red boxes.}\protect\\\hspace{\textwidth}
   \emph{Right:}\hfill
   \parbox[t]{.95\linewidth}{MVDR window amplitude and phase responses computed from the 40x40 pixel groups. The responses are overlayed each other and the amount of overlap is colored using a logarithmic scale. The size of the pixel groups were chosen ad-hoc for the histograms to be visually invariant to a shift in position within the same region. Since each pixel is pre-delayed into focus the unsteered responses all have their center at broadside. The dashed red lines at -13\,dB and -43\,dB marks the peak sidelobe levels of an unsteered rectangular and Hamming window, respectively. Note how the responses are more or less symmetric, with very little steering in the shadow, moderate steering in speckle and steering within roughly 3\,dB in highlight. The phase varies most in the highlight region where we see the highest contrast.} }\label{mvdr_selected_windows}
\fi%

\end{figure*}

\ifPhdDoc
   \begin{figure*}[tbp]\centering%
   \includegraphics[width=\linewidth]{gfx/fig4.pdf}%
   \caption{\emph{Determining Kaiser parameter boundaries}: LCA images of the resolution test cross and anchor created with a large window database, but where the upper bounds for $\beta$ and $\phi$ are varied. The upper left image is equal to DAS with a rectangular window. For all images we measure the lateral distance $\Delta x$ between the two \protect\minus{}3\,dB points of the anchor (red object). These are specified relatively to the reference distance  $\Delta x_\text{ref}$ from the upper left DAS image.
   \\[.5\baselineskip]
   \textbf{Upper bound $\beta$:} Observe that LCA gets better at suppressing sidelobes in the image as we increase the upper bounds for $\beta$. \Fig{mvdr_selected_windows} suggests that MVDR prefers windows with sidelobe levels lower than that of Kaiser with $\beta=2$, but here we observe further improvement going to $\beta=5$.
   \\[.5\baselineskip]
   \textbf{Upper bound $\phi$:} As we increase the upper bound of the steering $\phi$, we also increase the lateral image resolution.
   }
\else
   \begin{figure*}[t]%
   \includegraphics[width=\textwidth]{gfx/buske4_online.pdf}%
   \caption{\emph{Determining Kaiser parameter boundaries}: LCA images of the resolution test cross and anchor created with a large window database, but where the upper bounds for $\beta$ and $\phi$ are varied. The upper left image is equal to DAS with a rectangular window. For all images we measure the lateral distance $\Delta x$ between the two \protect\minus{}3\,dB points of the anchor (red object). These are specified relatively to the reference distance  $\Delta x_\text{ref}$ from the upper left DAS image.
   \newline
   \emph{Upper bound $\beta$:}\hfill
   \parbox[t]{.89\linewidth}{Observe that LCA gets better at suppressing sidelobes in the image as we increase the upper bounds for $\beta$. \Fig{mvdr_selected_windows} suggests that MVDR prefers windows with sidelobe levels lower than that of Kaiser with $\beta=2$, but here we observe further improvement going to $\beta=5$.}\newline
   \emph{Upper bound $\phi$:}\hfill
   \parbox[t]{.89\linewidth}{As we increase the upper bound of the steering $\phi$, we also increase the lateral image resolution. }
   }
\fi%
\label{oversampling_mosaic_bounds}
\end{figure*}

@@

\ifPhdDoc
   \begin{figure*}[tb]\centering%
   \includegraphics[width=\linewidth]{gfx/fig6.pdf}%
\else
   \begin{figure*}[t]%\centering%
   \includegraphics[width=\textwidth]{gfx/buske6_online.pdf}%
\fi
\caption{\emph{LCA images using different window database sizes}. The window boundaries are the same. The upper left image is identical to a rectangularly weighted DAS. Observe that finer sampling of the $\beta$-range improves sidelobe suppression but leaves resolution unchanged. Adding more steering-variations improves both sidelobe suppression and resolution. However, using more than  $N_\beta=2$ window types and $N_\phi=3$ steering angles makes minimal difference.}\label{oversampling_mosaic}
\end{figure*}

@@

\ifPhdDoc
\clearpage
\appendix
\renewcommand\thesection{\Roman{section}}
\else
\appendices
\fi
